RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface

### 2023-10-22 review/response.tex

	\point All simulation results and respective optimization solutions are offered with relatively small number of K and M; some discussion on ways to extend the methodology for larger networks and loads should be helpful.
	\reply {Thank you for the suggestion. The main limitations for massive RIScatter are the energy detection and the dynamic programming algorithm. For $K$ nodes each with $M$ states, there are a total of $L = M^K$ energy decision regions to design. The candidate threshold set $\mathcal{T}$ should be even finer, which results in a very fast growth of the computational complexity ($\mathcal{O}\bigl(L^2(\mathrm{card}(\mathcal{T})-L)\bigr)$ for SMAWK and $\mathcal{O}\bigl(\mathrm{card}(\mathcal{T})L\log(\mathrm{card}(\mathcal{T})L)\bigr)$ for bisection). To support massive RIScatter networks with large number of nodes and states, one possible future direction is to consider backscatter detection over the received signal domain rather than energy domain, where multi-antenna \cite{Liu2022c} and learning-based approaches can be promising. We have added this to Section~\ref{m-sc:conclusion} of the revised manuscript.}

	\point Finally, the list of references is perhaps incomplete; many references do not include publication venues, while prior art backscatter radio, including coherent as well as non-coherent detection, structural mode, receiverless tags etc., both in terms of theory as well as experimentation, are not given. For example see work that bridges backscatter radio and RIS, including theory and experimental results for any number of tags and loads in the following: "Intelligently Wireless Batteryless RF-Powered Reconfigurable Surface: Theory, Implementation \& Limitations", IEEE Transactions on Wireless Communications (TWC), available as early access in ieeexplore, Nov. 2022, conference version available at IEEE Globecom 2021.
	\reply {We agree with the reviewer that the reference list could be improved. The current state of the art in BackCom is indeed very rich and diverse.  In the previous version of our manuscript, we only introduced papers that use RIS for backscatter modulation. In contrast, the recommended reference exploited commodity RFID tags, powered and controlled by a software-defined radio reader, to perform passive beamforming towards a legacy user at a different frequency. It validates the feasibility of using batteryless devices to adaptively enhance the SNR of the primary link. This reference makes the literature review more comprehensive, and we have added it in page~\pageref{m-cm:2.5} of the revised manuscript.}
\end{reviewer}

### 2023-10-22 arxiv.tex
:triangular_flag_on_post: JSAC 231022

\begin{abstract}
	\gls{bc} nodes harvest energy from and modulate information over external electromagnetic waves.
	\gls{ris} adapts its phase shift response to alter channel strength in specific directions.
	In this paper, we show how those two seemingly different technologies (and their derivatives) can be unified into one architecture called RIScatter.
	RIScatter consists of dispersed or co-located scatter nodes, whose reflection states are adapted to partially modulate their information and partially engineer the wireless channel.
	The key is to render the probability distribution of reflection states as a joint function of the information source, \gls{csi}, and relative priority of coexisting links.
	This enables RIScatter to softly bridge \gls{bc} and \gls{ris}; reduce to either under specific setup; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
	We also propose a low-complexity \gls{sic}-free receiver that exploits the properties of RIScatter.
	For a single-user multi-node network, we characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at scatter nodes, the active beamforming at the \gls{ap}, and the energy decision regions at the user.
	Simulations demonstrate RIScatter nodes can recycle surrounding radios for backscatter modulation and passive beamforming.
\end{abstract}

@@

	As a special case of \gls{cr}, active and passive transmissions coexist and interplay in \gls{ambc} and \gls{sr}.
	Such a coexistence is classified into commensal (overlay), parasitic (underlay), and competitive (interfering) paradigms, and their achievable rate and outage performance were investigated in \cite{Guo2019b,Ding2020}.
	The achievable rate and optimal input distribution for binary-input \gls{ambc} are investigated in \cite{Qian2019b}, but its impact on the primary link is omitted.
	% For binary-input \gls{ambc},  are investigated in \cite{Qian2019b}, but the authors did not consider its impact on the primary link.
	% The \gls{ber} performance of \gls{ml}, linear, and \gls{sic} receivers are derived over flat fading channels \cite{Yang2018}.
	% The authors of \cite{Hassani2023} analyzed the energy efficiency and achievable rate region for an \gls{ambc}-aided multi-user downlink \gls{noma} system.
	In \cite{Hassani2023}, the authors analyzed the energy efficiency and achievable rate region for an \gls{ambc}-aided multi-user downlink \gls{noma} system.
	However, they assumed equal symbol duration and perfect synchronization for the coexisting links.
	Importantly, active-passive coexisting networks have three special and important properties:
	\begin{enumerate}
		\item Primary and backscatter symbols are superimposed by \emph{double modulation} (i.e., multiplication coding);
		\item Backscatter signal strength is much weaker than primary due to \emph{double fading};
		\item The spreading factor (i.e., backscatter symbol duration over primary) is usually large\footnote{The load-switching interval of low-power backscatter modulators is usually \num{0.1} to \qty{10}{\us} \cite{Torres2021}, accounting for a typical spreading factor between \num{10} and \num{e3}.}.
	\end{enumerate}
	The second property motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Dai2023} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
	During primary decoding, the backscatter signal can be modelled as channel uncertainty or multiplicative interference, when the spreading factor is large or small.
	Decoding each backscatter symbol also requires multiple \gls{sic} followed by a \gls{mrc} over primary blocks, which is operation-intensive and \gls{csi}-sensitive.
	Under those assumptions, the achievable rate region of cell-free \gls{sr} is characterized in \cite{Dai2023}.
	When the spreading factor is sufficiently large, the primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding with known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart such that both links are approximately interference-free \cite{Long2020a}.
	However, this assumption severely limits the backscatter throughput.

@@

	On the other hand, static \gls{ris} that employs fixed reflection pattern per channel block has been extensively studied in wireless communication, sensing, and power literature \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
	Dynamic \gls{ris} performs time sharing between different phase shifts and introduces artificial channel diversity within each channel block.
	The idea was first proposed to fine-tune the \gls{ofdm} resource blocks \cite{Yang2020}, then extended to the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
	However, dynamic \gls{ris} carries no information because the reflection state at a specific time is known to the receiver.
	\gls{ris} can also be used as an information source, and prototypes have been developed for \gls{psk} \cite{Tang2019a} and \gls{qam} \cite{Dai2020a}.
	From an information-theoretic perspective, the authors of \cite{Karasik2020} reported that joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided finite-input channel, and using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally rate-suboptimal.
	This inspired \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall \gls{ris} design.
	In particular, \emph{symbol level precoding} maps the information symbols to the optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes the information symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between the reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} employs dedicated reflection elements (resp. information elements) for passive beamforming (resp. backscatter modulation) \cite{Hu2021a}.
	Those \gls{ris}-based backscatter modulation schemes incur advanced hardware architecture and high optimization complexity.
	In contrast, \cite{Vardakis2023} exploits commodity \gls{rfid} tags, powered and controlled by a software-defined radio reader at a different frequency, to perform passive beamforming (but no backscatter modulation) towards a legacy user. \label{cm:2.5}
	% The authors demonstrated the feasibility of using batteryless devices to adaptively enhance the \gls{snr} of a primary link, but did not consider backscatter modulation at.
	Most relevant literature considers either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes, or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit the \gls{csi} and properties of active-passive coexisting networks.
	Those problems are addressed in this paper and the contributions are summarized below.

	\emph{First,} we propose RIScatter as a novel protocol that unifies \gls{bc} and \gls{ris} by adaptive reflection state (backscatter input) distribution design.
	The concept is shown in Fig.~\subref*{fg:riscatter}, where one or more RIScatter nodes ride over an active transmission to simultaneously modulate their information and engineer the wireless channel.
	A co-located receiver cooperatively decodes both coexisting links.
	Each reflection state is simultaneously an information codeword and a passive beamforming codeword.
	The reflection pattern over time is semi-random and guided by the input probability assigned to each state.
	This probability distribution is carefully designed to incorporate the backscatter information, \gls{csi}, and \gls{qos}\footnote{\gls{qos} refers to the relative priority of the primary link.\label{fn:qos}}.
	Such an adaptive channel coding boils down to the degenerate distribution of \gls{ris} when the primary link is prioritized, and outperforms the uniform distribution of \gls{bc} (by accounting the \gls{csi}) when the backscatter link is prioritized.
	Table~\ref{tb:scattering_applications} compares RIScatter to \gls{bc} and \gls{ris}.
	However, two major challenges for RIScatter are the receiver design and input distribution design.
	This is the first paper to unify \gls{bc} and \gls{ris} from the perspective of input distribution.

@@

\begin{section}{RIScatter}
	\label{sc:riscatter}
	\begin{subsection}{Principles}
		\label{sc:principles}
		\gls{rf} wave scattering or reflecting are often manipulated by passive antennas or programmable metamaterial \cite{Liang2022}.
		The former receives the impinging signals and reradiates some back to the space, while the latter reflects at the space-cell boundary and mainly applies a phase shift.
		In the scattered signal, the structural mode component depends on the scatterer geometry and material.
		Its impact is usually modelled as part of environment multipath \cite{Thomas2012,Liang2020}, or simply a baseband \gls{dc} offset when the impinging signal is a \gls{cw} \cite{Boyer2014}.
		On the other hand, the antenna mode component depends on the impedance mismatch and is widely exploited in scattering applications.
		For an antenna (resp. metamaterial) scatterer with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is \cite{VanHuynh2017,Liang2022}
		\begin{equation}
			\Gamma_m = \frac{Z_m - Z^*}{Z_m + Z},
			\label{eq:reflection_coefficient}
		\end{equation}
		where $Z_m$ is the antenna load (resp. metamaterial cell) impedance at state $m$, and $Z$ is the antenna input (resp. medium characteristic) impedance.
		Specifically,
		\begin{itemize}
			\item \gls{bc}: The scatterer is an information source with random reflection pattern over time.
			The reflection coefficient is used merely as an information codeword \cite{Thomas2012a}
			\begin{equation}
				\Gamma_m = \alpha_m \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
				\label{eq:backscatter_modulation}
			\end{equation}
			where $\alpha_m \in \mathbb{I}$ is the amplitude scattering ratio at state $m$, and $c_m$ is the corresponding constellation point.
			\item \gls{ris}: The scatterer is a channel shaper with deterministic reflection pattern over time.
			The reflection coefficient is used merely as a passive beamforming codeword \cite{Wu2018}
			\begin{equation}
				\Gamma_m = \alpha_m \exp(j \theta_m),
				\label{eq:passive_beamforming}
			\end{equation}
			where $\theta_m$ is the phase shift at state $m$.\footnote{Most papers assume $\alpha_m = \alpha$, with $\alpha \ll 1$ for \gls{bc} and $\alpha=1$ for \gls{ris}.\label{fn:scattering_ratio}}
		\end{itemize}

		RIScatter generalizes \gls{bc} and \gls{ris} from a probabilistic perspective.
		Each reflection coefficient simultaneously acts as an information codeword and a passive beamforming codeword.
		As shown in Fig.~\ref{fg:scatter_comparison}, the reflection pattern of each RIScatter node over time is semi-random and guided by the input probability assigned to each state.
		This probability distribution is carefully designed to incorporate the backscatter information, \gls{csi}, and \gls{qos}, in order to strike a balance between backscatter modulation and passive beamforming.
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/input_distribution.tex}
				}
				\label{fg:input_distribution}
			}
			\\
			\subfloat[Reflection Pattern]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/time_structure.tex}
				}
				\label{fg:time_structure}
			}
			\caption{
				Input distribution and reflection pattern of scattering applications.
				``PB'', ``BB'', and ``CB'' refer to primary symbol block, backscatter symbol block, and channel block, respectively.
				Shadowing means presence of primary link.
				In this example, the optimal passive beamformer corresponds to state \num{2}.
				The spreading factor is \num{4} for RIScatter and \num{8} for \gls{ambc}/\gls{sr}.
				\gls{bc} and \gls{ris} can be viewed as extreme cases of RIScatter, where the input distribution boils down to uniform and degenerate, respectively.
			}
			\label{fg:scatter_comparison}
		\end{figure}
		\begin{remark}
			Unlike dynamic \gls{ris} that simply performs a time sharing between reflection states, RIScatter conveys additional information by randomizing the reflection pattern over time while still guaranteeing the probability of occurrence of each state.
			Upon successful backscatter detection, the impact of RIScatter nodes on the primary link can be modelled as dynamic passive beamforming.
			\label{re:dynamic_passive_beamforming}
		\end{remark}

@@

		\begin{remark}
			We have assumed Gaussian codebook for the primary source and finite support for the backscatter nodes, since they are relatively practical and widely adopted in relevant literatures.
			The proposed framework is extendable to non-Gaussian primary source, and the conditional \gls{pdf} \eqref{eq:energy_distribution} can be approximated using \gls{clt} for large $N$.
			\label{re:non_gaussian}
		\end{remark}

@@

\begin{section}{Simulation Results}
	\label{sc:simulation_results}
	In this section, we provide numerical results to evaluate the proposed algorithms.
	We assume the AP-user distance is \qty{10}{m} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius $r$.
	The \gls{ap} is with maximum average transmit power $P=\qty{36}{dBm}$ and all nodes employs $M$-\gls{qam} with $\alpha=0.5$.
	For all channels involved, we consider a distance-dependent path loss model
	\begin{equation}
		L(d) = L_0 \biggl(\frac{d_0}{d}\biggr)^\gamma,
	\end{equation}
	together with a Rician fading model
	\begin{equation}
		\boldsymbol{H} = \sqrt{\frac{\kappa}{1+\kappa}} \bar{\boldsymbol{H}} + \sqrt{\frac{1}{1+\kappa}} \tilde{\boldsymbol{H}},
	\end{equation}
	where $d$ is the transmission distance, $L_0=-\qty{30}{dB}$ is the reference path loss at $d_0=\qty{1}{m}$, $\kappa$ is the Rician K-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with standard \gls{iid} \gls{cscg} entries.
	We choose $\gamma_{\text{D}}=2.6$, $\gamma_{\text{F}}=2.4$, $\gamma_{\text{B}}=2$, and $\kappa_{\text{D}}=\kappa_{\text{F}}=\kappa_{\text{B}}=5$ for direct, forward and backward links.
	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the $1-\varepsilon$ confidence bounds of edge hypotheses (i.e., lower bound of $x_1$ and upper bound of $x_L$).
	We set $b=9$ and $\varepsilon=\num{e-3}$.
	All achievable rate regions are averaged over \num{e3} channel realizations.

>>>>

\begin{abstract}
	\gls{bc} nodes harvest energy from and modulate information over external carriers.
	\gls{ris} adapts phase shift response to alter channel strength in specific directions.
	In this paper, we unify those two seemingly different technologies (and their derivatives) into one architecture called RIScatter.
	RIScatter is a batteryless cognitive radio that recycles ambient signal in an adaptive and customizable manner, where dispersed or co-located scatter nodes partially modulate their information and partially engineer the wireless channel.
	The key is to render the probability distribution of reflection states as a joint function of the information source, \gls{csi}, and relative priority of coexisting links.
	This enables RIScatter to softly bridge \gls{bc} and \gls{ris}; reduce to either in special cases; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
	We also propose a low-complexity \gls{sic}-free receiver that exploits the properties of RIScatter.
	For a single-user multi-node network, we characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at scatter nodes, the active beamforming at the \gls{ap}, and the energy decision regions at the user.
	Simulations demonstrate RIScatter nodes can shift between backscatter modulation and passive beamforming.
\end{abstract}

@@

	As a special case of \gls{cr}, active and passive transmissions coexist and interplay in \gls{ambc} and \gls{sr}.
	Such a coexistence is classified into commensal (overlay), parasitic (underlay), and competitive (interfering) paradigms, and their achievable rate and outage performance were investigated in \cite{Guo2019b,Ding2020}.
	The achievable rate and optimal input distribution for binary-input \gls{ambc} were investigated in \cite{Qian2019b}, but its impact on the primary link was omitted.
	% For binary-input \gls{ambc},  are investigated in \cite{Qian2019b}, but the authors did not consider its impact on the primary link.
	% The \gls{ber} performance of \gls{ml}, linear, and \gls{sic} receivers are derived over flat fading channels \cite{Yang2018}.
	% The authors of \cite{Hassani2023} analyzed the energy efficiency and achievable rate region for an \gls{ambc}-aided multi-user downlink \gls{noma} system.
	In \cite{Hassani2023}, the authors analyzed the energy efficiency and achievable rate region for an \gls{ambc}-aided multi-user downlink \gls{noma} system.
	However, they assumed equal symbol duration and perfect synchronization for the coexisting links.
	Importantly, active-passive coexisting networks have three special and important properties:
	\begin{enumerate}
		\item Primary and backscatter symbols are superimposed by \emph{double modulation} (i.e., multiplication coding);
		\item Backscatter signal strength is much weaker than primary due to \emph{double fading};
		\item The spreading factor (i.e., backscatter symbol duration over primary) is usually large\footnote{The load-switching interval of low-power backscatter modulators is usually \num{0.1} to \qty{10}{\us} \cite{Torres2021}, accounting for a typical spreading factor between \num{10} and \num{e3}.}.
	\end{enumerate}
	The second property motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Hassani2023,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Dai2023} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
	During primary decoding, the backscatter signal can be modelled as channel uncertainty or multiplicative interference, when the spreading factor is large or small.
	Decoding each backscatter symbol also requires multiple \gls{sic} followed by a \gls{mrc} over primary blocks, which is operation-intensive and \gls{csi}-sensitive.
	Under those assumptions, the achievable rate region of cell-free \gls{sr} was characterized in \cite{Dai2023}.
	When the spreading factor is sufficiently large, the primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding with known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart such that both links are approximately interference-free \cite{Long2020a}.
	However, this assumption severely limits the backscatter throughput.

@@

	On the other hand, static \gls{ris} that employs fixed reflection pattern per channel block has been extensively studied in wireless communication, sensing, and power literature \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
	Dynamic \gls{ris} performs time sharing between different phase shifts and introduces artificial channel diversity within each channel block.
	The idea was first proposed to fine-tune the \gls{ofdm} resource blocks \cite{Yang2020}, then extended to the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
	However, dynamic \gls{ris} carries no information because the reflection state at a specific time is known to the receiver.
	\gls{ris} can also be used as an information source, and prototypes have been developed for \gls{psk} \cite{Tang2019a} and \gls{qam} \cite{Dai2020a}.
	From an information-theoretic perspective, the authors of \cite{Karasik2020} reported that joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided finite-input channel, and using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally rate-suboptimal.
	This inspired \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall \gls{ris} design.
	In particular, \emph{symbol level precoding} maps the information symbols to the optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes the information symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between the reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} employs dedicated reflection elements (resp. information elements) for passive beamforming (resp. backscatter modulation) \cite{Hu2021a}.
	Those \gls{ris}-based backscatter modulation schemes incur advanced hardware architecture and high optimization complexity.
	In contrast, \cite{Vardakis2023} exploited commodity \gls{rfid} tags, powered and controlled by a software-defined radio reader at a different frequency, to perform passive beamforming (but no backscatter modulation) towards a legacy user. \label{cm:2.5}
	% The authors demonstrated the feasibility of using batteryless devices to adaptively enhance the \gls{snr} of a primary link, but did not consider backscatter modulation at.
	Most relevant literature considered either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes, or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit the \gls{csi} and properties of active-passive coexisting networks.
	Those problems are addressed in this paper and the contributions are summarized below.

	\emph{First,} we propose RIScatter as a novel protocol that unifies \gls{bc} and \gls{ris} by adaptive reflection state (backscatter input) distribution design.
	The concept is shown in Fig.~\subref*{fg:riscatter}, where one or more RIScatter nodes ride over an active transmission to simultaneously modulate their information and engineer the wireless channel.
	A co-located receiver cooperatively decodes both coexisting links.
	Each reflection state is simultaneously a passive beamforming codeword and part of information codeword.
	The reflection pattern over time is semi-random and guided by the input probability assigned to each state.
	This probability distribution is carefully designed to incorporate the backscatter information, \gls{csi}, and \gls{qos}\footnote{\gls{qos} refers to the relative priority of the primary link.\label{fn:qos}}.
	Such an adaptive channel coding boils down to the degenerate distribution of \gls{ris} when the primary link is prioritized, and outperforms the uniform distribution of \gls{bc} (by accounting the \gls{csi}) when the backscatter link is prioritized.
	Table~\ref{tb:scattering_applications} compares RIScatter to \gls{bc} and \gls{ris}.
	However, two major challenges for RIScatter are the receiver design and input distribution design.
	This is the first paper to unify \gls{bc} and \gls{ris} from the perspective of input distribution.

@@

\begin{section}{RIScatter}
	\label{sc:riscatter}
	\begin{subsection}{Principles}
		\label{sc:principles}
		\gls{rf} wave scattering or reflecting are often manipulated by passive antennas or programmable metamaterial \cite{Liang2022}.
		The former receives the impinging signals and reradiates some back to the space, while the latter reflects at the space-cell boundary and mainly applies a phase shift.
		In the scattered signal, the structural mode component depends on the scatterer geometry and material.
		Its impact is usually modelled as part of environment multipath \cite{Thomas2012,Liang2020}, or simply a baseband \gls{dc} offset when the impinging signal is a \gls{cw} \cite{Boyer2014}.
		On the other hand, the antenna mode component depends on the impedance mismatch and is widely exploited in scattering applications.
		For an antenna (resp. metamaterial) scatterer with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is \cite{VanHuynh2017,Liang2022}
		\begin{equation}
			\Gamma_m = \frac{Z_m - Z^*}{Z_m + Z},
			\label{eq:reflection_coefficient}
		\end{equation}
		where $Z_m$ is the antenna load (resp. metamaterial cell) impedance at state $m$, and $Z$ is the antenna input (resp. medium characteristic) impedance.
		Specifically,
		\begin{itemize}
			\item \gls{bc}: The scatterer is an information source with random reflection pattern over time.
			The reflection coefficient is used merely as part of information codeword \cite{Thomas2012a}
			\begin{equation}
				\Gamma_m = \alpha_m \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
				\label{eq:backscatter_modulation}
			\end{equation}
			where $\alpha_m \in \mathbb{I}$ is the amplitude scattering ratio at state $m$, and $c_m$ is the corresponding constellation point.
			\item \gls{ris}: The scatterer is a channel shaper with deterministic reflection pattern over time.
			The reflection coefficient is used merely as a passive beamforming codeword \cite{Wu2018}
			\begin{equation}
				\Gamma_m = \alpha_m \exp(j \theta_m),
				\label{eq:passive_beamforming}
			\end{equation}
			where $\theta_m$ is the phase shift at state $m$.\footnote{Most papers assume $\alpha_m = \alpha$, with $\alpha \ll 1$ for \gls{bc} and $\alpha=1$ for \gls{ris}.\label{fn:scattering_ratio}}
		\end{itemize}

		RIScatter generalizes \gls{bc} and \gls{ris} from a probabilistic perspective.
		Each reflection coefficient simultaneously acts as a passive beamforming codeword and part of information codeword.
		As shown in Fig.~\ref{fg:scatter_comparison}, the reflection pattern of each RIScatter node over time is semi-random and guided by the input probability assigned to each state.
		This probability distribution is carefully designed to incorporate the backscatter information, \gls{csi}, and \gls{qos}, in order to strike a balance between backscatter modulation and passive beamforming.
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/input_distribution.tex}
				}
				\label{fg:input_distribution}
			}
			\\
			\subfloat[Reflection Pattern]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/time_structure.tex}
				}
				\label{fg:time_structure}
			}
			\caption{
				Input distribution and reflection pattern of scattering applications.
				``PB'', ``BB'', and ``CB'' refer to primary symbol block, backscatter symbol block, and channel block, respectively.
				Shadowing means presence of primary link.
				In this example, the optimal passive beamformer corresponds to state \num{2}.
				The spreading factor is \num{4} for RIScatter and \num{8} for \gls{ambc}/\gls{sr}.
				\gls{bc} and \gls{ris} can be viewed as extreme cases of RIScatter, where the input distribution boils down to uniform and degenerate, respectively.
			}
			\label{fg:scatter_comparison}
		\end{figure}
		\begin{remark}
			Unlike dynamic \gls{ris} that simply performs a time sharing between reflection states, RIScatter conveys additional information by randomizing the reflection pattern over time while still guaranteeing the probability of occurrence of each state.
			Upon successful backscatter detection, the impact of RIScatter nodes on the primary link can be modelled as dynamic passive beamforming.
			\label{re:dynamic_passive_beamforming}
		\end{remark}

@@

		\begin{remark}
			We have assumed Gaussian codebook for the primary source and finite support for the backscatter nodes, since they are relatively practical and widely adopted in relevant literatures \cite{Long2020a,Liang2020,Guo2019b,Qian2019b,Ding2020,Hassani2023,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Dai2023}.
			The proposed framework is extendable to non-Gaussian primary source, and the conditional \gls{pdf} \eqref{eq:energy_distribution} can be approximated using \gls{clt} for large $N$.
			\label{re:non_gaussian}
		\end{remark}

@@

\begin{section}{Simulation Results}
	\label{sc:simulation_results}
	In this section, we provide numerical results to evaluate the proposed algorithms.
	We assume the AP-user distance is \qty{10}{m} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius $r$.
	The \gls{ap} is with maximum average transmit power $P=\qty{36}{dBm}$ and all nodes employs $M$-\gls{qam} with $\alpha=0.5$.
	For all channels involved, we consider a distance-dependent path loss model
	\begin{equation}
		L(d) = L_0 \biggl(\frac{d_0}{d}\biggr)^\gamma,
	\end{equation}
	together with a Rician fading model
	\begin{equation}
		\boldsymbol{H} = \sqrt{\frac{\kappa}{1+\kappa}} \bar{\boldsymbol{H}} + \sqrt{\frac{1}{1+\kappa}} \tilde{\boldsymbol{H}},
	\end{equation}
	where $d$ is the transmission distance, $L_0=-\qty{30}{dB}$ is the reference path loss at $d_0=\qty{1}{m}$, $\kappa$ is the Rician K-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with standard \gls{iid} \gls{cscg} entries.
	We choose $\gamma_{\text{D}}=2.6$, $\gamma_{\text{F}}=2.4$, $\gamma_{\text{B}}=2$, and $\kappa_{\text{D}}=\kappa_{\text{F}}=\kappa_{\text{B}}=5$ for direct, forward and backward links.
	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the $1-\varepsilon$ confidence bounds of edge hypotheses (i.e., lower bound of $x_1$ and upper bound of $x_L$).
	We set $b=9$ and $\varepsilon=\num{e-3}$.
	All achievable rate regions are averaged over \num{e3} channel realizations.\footnote{The code is publicly available at \url{https://github.com/snowztail/riscatter/}.}
